---
title: "03-seeking-help"
author: "Reid Otsuji"
date: "3/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading Help files
* R, and every package, provide help files for functions. 
* The general syntax to search for help on any function, `function_name`, from a specific function that is in a package loaded into your namespace (your interactive R session):

```{r eval=FALSE}
?function_name
help(function_name)
```

* This will load up a help page in RStudio (or as plain text in R by itself).


Each help page is broken down into sections:

1. **Description:** An extended description of what the function does.
Usage: The arguments of the function and their default values.
2. **Arguments:** An explanation of the data each argument is expecting.
3. **Details:** Any important details to be aware of.
4. **Value:** The data the function returns.
5. **See Also:** Any related functions you might find useful.
6. **Examples:** Some examples for how to use the function.

Different functions might have different sections, but these are the main ones you should be aware of.

# Special Operators

To seek help on special operators, use quotes:

```{r eval=FALSE}
?"<-"
```


# Getting help on packages

Many packages come with **“vignettes”**: tutorials and extended example documentation.    
* Without any arguments, `vignette()` will list all vignettes for all installed packages;     
* `vignette(package="package-name")` will list all available vignettes for package-name, and     
* `vignette("vignette-name")` will open the specified vignette.

If a package doesn’t have any vignettes, you can usually find help by typing `help("package-name")`.


## When you kind of remember the function
* If you’re not sure what package a function is in, or how it’s specifically spelled you can do a fuzzy search:
```{r eval=FALSE}
??function_name
```

# When you have no idea where to begin
* If you don’t know what function or package you need to use **CRAN Task Views** is a specially maintained list of packages grouped into fields. 
This can be a good starting point.

**show this**
http://cran.at.r-project.org/web/views

## When your code doesn’t work: seeking help from your peers

* If you’re having trouble using a function, 9 times out of 10, the answers you are seeking have already been answered on **Stack Overflow**.     
You can search using the `[r]` tag.

https://stackoverflow.com/

or Google


Show the R cheat sheets - recommend downloading for future reference     
**R Cheat Sheets**
https://www.rstudio.com/resources/cheatsheets/ 














